### 2019-03-20 thesis_proposal_1/Chapters/2_ProblmemDefinitionAndMotivation.tex
landscape pages

% Describe the current situation of this problem.
% identifying the obstacles and the possible applications of your research.
% background of the problem (e.g. origins, previous attempts, etc.). 
% State the problem in detail mentioning all relative aspects, variables, relationships,
% stressing on the importance of finding a solution to the problem.

Carbon nanowires have been fabricated with a photoresist by multiple-photon polymerization techniques. However little is known about polymers that can produce conductive carbon nanowires after pyrolysis. In the past years photon polymerization processes have been apllied to the fabrication of nano-structures with the use of a photoresist. \cite{Boer2014} Photon polymerization techniques deliver patterning resolutions with nano-scale tolerances for the production of highly detailed structures. \cite{Hribar2014} Normally Photon polymerization processes can only produce small objects and the resins are often toxic. \cite{Ovsianikov2012}

On the other hand, electrospinning has been acknowledged for as a process with promising results at nano-structure fabrication \cite{Boer2014}, yet there is little research regarding the implementation of electrospinning for the fabrication of carbon nano-wires. Electrospinning has the potential to be a more straightforward process for the design and fabrication of nano-structures, as it can achieve mass scale manufacturing in a continuous, simple and reproducible manner.

Since electrospinning is to be a better alternative for carbon nano-wire synthesis processes, for that purpose, it is required to develop polymer solutions that can be electrospun by near-field electrospinning (NFES) or electromechanic spinning, photopolymerized and pyrolyzed into conducting carbon nanowires. Carbon nano-materials have been subjected to research due to their various potential applications in diverse areas that take advantage of the nano-scale properties. \cite{Siddiqui2019} Carbon nano-materials are suitable for the catalysis, adsorption, carbon capture, energy and hydrogen storage, drug delivery, bio-sensing and cancer detection. \cite{Siddiqui2019} However most application are not currently feasible  due to the lack of a continuous, simple and reproducible fabrication method. With the newly required polymer solution, it would be possible to produce carbon nano-wires in large quantities, and therefore more application will become feasible.

>>>>

\subsubsection*{\color{mygray}[Chapter ready for review]}
% Describe the current situation of this problem.
% identifying the obstacles and the possible applications of your research.
% background of the problem (e.g. origins, previous attempts, etc.). 
% State the problem in detail mentioning all relative aspects, variables, relationships,
% stressing on the importance of finding a solution to the problem.

Carbon nanowires have been fabricated with a photoresist by multiple-photon polymerization techniques. However little is known about polymers that can produce conductive carbon nano-wires after pyrolysis. In the past years photon polymerization processes have been applied to the fabrication of nano-structures with the use of a photoresist. \cite{Boer2014} Photon polymerization techniques deliver patterning resolutions with nano-scale tolerances for the production of highly detailed structures, \cite{Hribar2014} However, it is typical of photon polymerization processes to yield small objects with waste resins that are often toxic. \cite{Ovsianikov2012}

On the other hand, electrospinning has been acknowledged for as a process with promising results at nano-structure fabrication \cite{Boer2014}, yet there is little research regarding the implementation of electrospinning for the fabrication of carbon nano-wires. Electrospinning has the potential to be a more straightforward process for the design and fabrication of nano-structures, as it can achieve mass scale manufacturing in a continuous, simple and reproducible manner. \cite{Cardenas2017} shows that electrospinning can be implemented with ease for carbon nano-wire synthesis. Mechano-electrospinning, a new variant of electrospinning shows promising results in the production of ordered carbon nano-wires. As stated in \cite{Cardenas2017}, mechano-electrispinning is an early technology invention, and brings new challenges, such as the reproducibility of carbon nano-wire production.

Since electrospinning seems to be a better alternative for carbon nano-wire synthesis processes; and for that purpose of its implementation, it is required to develop polymer solutions that can be mechano-electrospun, photopolymerized and pyrolyzed into conducting carbon nano-wires. Carbon nano-materials have been subjected to research due to their various potential applications in diverse areas that take advantage of the nano-scale properties. \cite{Siddiqui2019} Carbon nano-materials are suitable for the catalysis, adsorption, carbon capture, energy and hydrogen storage, drug delivery, bio-sensing and cancer detection. \cite{Siddiqui2019} However most application are not currently feasible due to the lack of a continuous, simple and reproducible fabrication method. With the newly designed polymer solution, it would be possible to produce carbon nano-wires in large quantities, and therefore more applications will become feasible.

### 2019-03-20 thesis_proposal_1/main.tex
thesis proposal progress
proposal in preogress
landscape pages

\documentclass[
% The default document font size, options: 10pt, 11pt, 12pt
11pt, 
% Two side (alternating margins) for binding by default, uncomment to switch to one side
%oneside,
% ngerman for German
english,
% Single line spacing, alternatives: onehalfspacing or doublespacing
singlespacing,
% Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
%draft,
% If the document is onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
%nolistspacing,
% Uncomment to add the list of figures/tables/etc to the table of contents
%liststotoc,
% Uncomment to add the main table of contents to the table of contents
%toctotoc,
% Uncomment to add space between paragraphs
parskip,
% Uncomment to not load the hyperref package
%nohyperref,
% Uncomment to get a line under the header
headsepline,
% Uncomment to place the chapter title next to the number on one line
%chapterinoneline,
% Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
%consistentlayout,
% The class file specifying the document structure
]{MastersDoctoralThesis}

@@

% Use the bibtex backend with the authoryear citation style (which resembles APA)
\usepackage[backend=biber,style=authoryear,natbib=true]{biblatex}
% MLA, APA, or IEEE? - https://www.overleaf.com/learn/latex/Biblatex_citation_styles
%\usepackage[style=apa, backend=biber]{biblatex}

% The filename of the bibliography
\addbibresource{example.bib}

@@

@@

% Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\thesistitle{Design of Polymer Solutions for the Fabrication of Conducting Carbon Nano-wires}

@@

\HRule \\[0.5cm]                            % Horizontal line
{\huge \bfseries \ttitle\par}\vspace{0.25cm} % Thesis title
\HRule \\[0.5cm]                            % Horizontal line

@@

\emph{Co-advisor and\\Director of Program:} \\
% Supervisor name - remove the \href bracket to remove the link
\href{https://www.medinadora.com/}{\cosupname}
%\cosupname
\end{flushright}
\end{minipage}\\[2cm]

@@

\large \textit{A thesis proposal submitted in fulfillment of the requirements\\ for the degree of
% University requirement text
\degreename}\\[0.3cm]
\textit{in}\\[0.4cm]
% Research group name and department name
\groupname\\\deptname\\[2cm]

@@

\bigskip
\bigskip
\bigskip
\bigskip
\bigskip

@@

\bigskip
\bigskip
\bigskip
\bigskip
\bigskip

\noindent \rule[0.5em]{15em}{0.5pt}\\ % This prints a line for the signature
%\href{http://www.alanaguirre.com}{\supname}
1st committee member name\\
1st committee member institution\\
\emph{Committee Member}

\bigskip
\bigskip
\bigskip
\bigskip
\bigskip

\noindent \rule[0.5em]{15em}{0.5pt}\\ % This prints a line for the signature
%\href{http://www.alanaguirre.com}{\supname}
2nd committee member name\\
2nd committee member institution\\
\emph{Committee Member}

@@

@@

>>>>

\documentclass[
% The default document font size, options: 10pt, 11pt, 12pt
11pt, 
% Two side (alternating margins) for binding by default, uncomment to switch to one side
%oneside,
% ngerman for German
english,
% Single line spacing, alternatives: singlespacing, onehalfspacing or doublespacing
onehalfspacing,
% Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
%draft,
% If the document is nolistspacing, onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
onehalfspacing,
% Uncomment to add the list of figures/tables/etc to the table of contents
%liststotoc,
% Uncomment to add the main table of contents to the table of contents
%toctotoc,
% Uncomment to add space between paragraphs
parskip,
% Uncomment to not load the hyperref package
%nohyperref,
% Uncomment to get a line under the header
headsepline,
% Uncomment to place the chapter title next to the number on one line
chapterinoneline,
% Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
%consistentlayout,
% The class file specifying the document structure
]{MastersDoctoralThesis}

@@

% Use tu justify paragraphs
\usepackage{ragged2e}

% Use the bibtex backend with the authoryear citation style (which resembles APA)
\usepackage[backend=biber,natbib=true]{biblatex}
% MLA, APA, or IEEE? - https://www.overleaf.com/learn/latex/Biblatex_citation_styles
%\usepackage[style=apa, backend=biber]{biblatex}

% The filename of the bibliography
\addbibresource{mainBiblio.bib}

@@

% to set default colours
\usepackage{xcolor}
\definecolor{mygray}{gray}{0.5}

% for gantt charts
\usepackage{tikz}
\usepackage{gantt}

\usepackage{lscape}

@@

% Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\thesistitle{Graphitic carbon suspended nano-wires synthesis through mechanoelectrospinning of photocrosslinkable polymers}

@@

\HRule \\%[0.5cm]                            % Horizontal line
{\huge \bfseries \ttitle\par}\vspace{0.0cm} % Thesis title
\HRule \\[0.5cm]                            % Horizontal line

@@

\emph{Co-advisor and\\Director of Program:} \\
% Supervisor name - remove the \href bracket to remove the link
\href{https://www.medinadora.com/}{\cosupname}
%\cosupname
\end{flushright}
\end{minipage}\\[0.5cm]

@@

\large \textit{A thesis proposal submitted in fulfillment of the requirements\\ for the degree of
% University requirement text
\degreename}\\[0.25cm]
\textit{in}\\[0.25cm]
% Research group name and department name
\groupname\\\deptname\\[1cm]

@@

\bigskip
\bigskip
\bigskip
\bigskip

@@

\bigskip
\bigskip
\bigskip
\bigskip

\noindent \rule[0.5em]{15em}{0.5pt}\\ % This prints a line for the signature
%\href{http://www.alanaguirre.com}{\supname}
Marc \textsc{Madou}\\
Tecnológico de Monterrey\\
\emph{Committee Member}

\bigskip
\bigskip
\bigskip
\bigskip

\noindent \rule[0.5em]{15em}{0.5pt}\\ % This prints a line for the signature
%\href{http://www.alanaguirre.com}{\supname}
Sergio Omar \textsc{Martínez} Chapa\\
Tecnológico de Monterrey\\
\emph{Committee Member}

@@

\setlength{\parskip}{1.5em} % Paragraph spacing
%\RaggedRight
{\fontsize{12}{15} \selectfont

@@

}
